### 2015-03-13 paper/paper.tex
Some more references to Griliches 1998

We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat.. A number of papers, such as \cite{AAC2014} , \cite{ABP2015} and \cite{BCJPV2015} have made use of patent citations. However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents.  \cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its meta information.
As \citep[p.~290]{MVS2010} note, 
\begin{quotation} 
``[...] the majority of studies and analyses undertaken in [patent and publication text search] focus on mere counts and/or quantitative attributes of relevant documents (e.g. number of publications, patents, number of references, number of citations); less attention is paid to analysis in which the content of the underlying documents is the focal point of attention."
\end{quotation}

@@

Figure~\ref{fig:summary_stats} shows a summary of the matches. The increase in keyword matches could be due to the general increase in the number of patents (see panel A) from around 70'000 to 320'000 patents. The share of distinct patents with at least one match (the light blue bars in figure~\ref{fig:summary_stats} ) has also steadily risen from 20 in 1991 to 30 percent in 2014.

@@

As a further option we could weigh this index by the number of times a patent has been cited by other patents using the data provided by \cite{HJT2001}, however correcting for the fact that older patents have been cited more often. Such a citation-weighted index could take the form $x_i = log(1+m_i) [1+log(1+\frac{c_i}{C_t})]$, where $c_i$ are the patent $i$'s citations over the whole period and $C_t$ are the total number of citations of patents in the same year over the whole period. A potential cost of including patent citations would be limiting the number of patents to the roughly 3 mio. patents and the time up to 2006 that \cite{HJT2001} (and later revisions) cover.

\section{Linking Patent Citations to Industries}
In order to use our patent data for economic analyses other than at the aggregate level, we need to match the patent classes with the industries where these patents are applied. In general, this is not an easy task since the same patent might be of use in various different industries. The industry to which the patent assignee belongs might not be informative in this context because many large companies - which are, in general, those companies most likely to innovate - are active in multiple different fields. Having warned about these possible shortcomings, we still believe that patent-industry matching yields meaningful insights.%\linebreak

@@

\subsection{Other possible uses of database not linked to employment}
Although not of immediate interest to us in the context of this research project, there are many other possible applications of the automation database, which could be the subject of future research projects: (1) automation and sectoral productivity: does technological change increase (labor) productivity more in some sectors than in others? (2) comparing U.S. automation patents to European automation patents (using additional data from the European Patent Office or other sources): where is automation higher? Are there sector-level differences and do these link to comparative advantage and/or institutional characteristics? (The political economy literature on varieties of capitalism suggests that U.S. firms should innovate more in IT, pharmaceutics, biotechnology and related sectors whereas continental European firms should innovate more in manufacturing.)

>>>>

We are not the first to analyze patent data: \cite{HJT2001} provide data on patent citations and link those to publicly-traded firms on Compustat. Patent citations differ from academic citations in that the patent examiner determines determine the novelty of the patent and the citations are therefore likely to be more objective than those in academic publications. A number of papers, such as \cite{AAC2014} , \cite{ABP2015} and \cite{BCJPV2015} have made use of patent citations. However, contrary to those papers, we concentrate on the patent's \textit{content}, not on its relation to other patents.  \cite{G1998} surveys the use of patents in economics and recommends a stronger use of the contents of patent documents, not only its aggregated meta information.
As \citep[p.~290]{MVS2010} note, 
\begin{quotation} 
``[...] the majority of studies and analyses undertaken in [patent and publication text search] focus on mere counts and/or quantitative attributes of relevant documents (e.g. number of publications, patents, number of references, number of citations); less attention is paid to analysis in which the content of the underlying documents is the focal point of attention."
\end{quotation}

@@

Figure~\ref{fig:summary_stats} shows a summary of the matches. The increase in keyword matches could be due to the general increase in the number of patents (see panel A) from around 70'000 to 320'000 patents. The share of distinct patents with at least one match (the light blue bars in figure~\ref{fig:summary_stats} ) has also steadily risen from 20 in 1991 to 30 percent in 2014. \cite{G1998}  remarks that there was a global reduction in patents granted (and only a minor reduction in applications) throughout the 1970s, the end of which can also be seen in our data. \cite{G1998} discusses the possibility of this being due to ``bureaucratic cycles".

@@

\cite{G1998} recommends weighting for the importance of patents. A such we could weigh this index by the number of times a patent has been cited by other patents using the data provided by \cite{HJT2001}, however correcting for the fact that older patents have been cited more often. Such a citation-weighted index could take the form $x_i = log(1+m_i) [1+log(1+\frac{c_i}{C_t})]$, where $c_i$ are the patent $i$'s citations over the whole period and $C_t$ are the total number of citations of patents in the same year over the whole period. A potential cost of including patent citations would be limiting the number of patents to the roughly 3 mio. patents and the time up to 2006 that \cite{HJT2001} (and later revisions) cover.

\section{Linking Patent Citations to Industries}
In order to use our patent data for economic analyses other than at the aggregate level, we need to match the patent classes with the industries where these patents are applied. In general, this is not an easy task since the same patent might be of use in various different industries. \cite{G1998} describes some of the difficulties faced when matching patents to industries. The industry to which the patent assignee belongs might not be informative in this context because many large companies - which are, in general, those companies most likely to innovate - are active in multiple different fields. Having warned about these possible shortcomings, we still believe that patent-industry matching yields meaningful insights.%\linebreak

@@

\subsection{Other possible uses of database not linked to employment}
Although not of immediate interest to us in the context of this research project, there are many other possible applications of the automation database, which could be the subject of future research projects: 
\begin{enumerate}
\item automation and sectoral productivity: does technological change increase (labor) productivity more in some sectors than in others? 
\item comparing U.S. automation patents to European automation patents (using additional data from the European Patent Office or other sources): where is automation higher? Are there sector-level differences and do these link to comparative advantage and/or institutional characteristics? (The political economy literature on varieties of capitalism suggests that U.S. firms should innovate more in IT, pharmaceutics, biotechnology and related sectors whereas continental European firms should innovate more in manufacturing.) 
\item one could also compare this patent index to aggregate total factor productivity. However, \cite{G1998} discusses the use of patents as an  ``output" index (like a technology frontier) vs an ``input" index (for example, to measure a firms research activities) and warns against interpreting changes in patent numbers in the time dimension.
\end{enumerate}
